Dynein walks like an Imperial AT-ST

### 2018-08-20 papers/paper/paper.tex
Add (very rough) methods section with onebound equations derivation

@@

>>>>

\matmethods{

  \subsection*{Onebound motion equations}
  Brownian Dynamics was used to describe the motion of each domain:

  \begin{equation}
    \dot{X_i} = \frac{1}{\gamma_i}\left(F^x_i + R^x_i\right)
  \end{equation}

  where $F^x_i$ is the force projection on coordinate $x$ of domain $i$, and $R^x_i$ the Brownian force. Expanding the force term and transforming position variables to polar coordinates yields the following:

  \begin{multline}
    \dot{X_i}\left(\theta_1, ..., \theta_n, \dot{\theta_1}, ..., \dot{\theta_n}\right) = \frac{1}{\gamma_i}\big(F(\theta_1, ..., \theta_n) + \\
    \lambda_i\left(X_{i+1}-X_i\right) + \lambda_{i-1}\left(X_i-X_{i-1}\right)R^x_i\big)
    \label{eq:ob-system}
  \end{multline}

  where the $\lambda$ terms are tension terms needed to maintain the rigid rod constraints. Each $X_i$ coordinate is related to the $\theta_j$ coordinates via the recursive formulas $X_1 = L_1\cos(\theta_1)$ and $X_{i>1} = L_i\cos(\theta_i)+L_{i-1}$ for x-coordinates and $Y_1 = 0$ and $Y_{i>1} = L_i\sin(\theta_i)+L_{i-1}$. Thus, each $\dot{X_i}$ term is linearly related to all $\dot{\theta_j}$ terms.\\

  There are $n$ unknown $\theta_j$ values and n unknown $\lambda$ values, totaling $2n$ unknown variables. There are $2n$ equations linear in $\dot{theta_j}$ and $\lambda_q$, $n$ each from the X and Y equations. The system of equations provided by Equation $\ref{eq:ob-system}$ was solved in Matlab, yielding equations for all $\dot{\theta_j}$.
}

@@

\showmatmethods
